### 2021-06-05 paper/calibration_and_estimation.tex
Add explanation how we handle weekend work contacts.
Some smallish updates; compile on Linux.
Add new results figures.

\begin{figure}[ht]
    \centering
    \includegraphics[width=0.9 \textwidth]{../figures/assortative_matching_probability_example.png}
    \caption{Distribution of random non-work contacts by age of participants.}
    \label{fig:assortativity}
    \figurenotes{
        The figure shows the distribution of random non-work contacts by age groups. A
        row shows the share of contacts a certain age group has with all other age
        groups. Higher values are colored in darker red tones. The diagonal represents
        the share of contacts with individuals from the same age group. }
\end{figure}

@@

In our empirical application we distinguish four groups of contact types: households,
education, work and other contacts. For households we assume that the individuals'
contacts in their households do not change over our estimation period. For nurseries,
preschools and schools we implement vacations as announced by the German federal states
as well as school closures. For the moment we ignore both emergency childcare and that
lack of childcare leads working parents to stay home.
%
% Schließung von Kindertagesstätten und Schulen: 37,4 Millionen ausgefallene Arbeitstage
% http://www.iab-forum.de/schul-und-kitaschliessungen-krankheit-quarantaene-die-coronabedingten-arbeitsausfaelle-der-erwerbstaetigen-steigen-auf-592-millionen-arbeitstage/
%
%
% https://www.sueddeutsche.de/politik/schulschliessung-lockdown-bildung-1.5190377:
% In allen Ländern geht trotz des Lockdowns ein erheblicher Anteil der Schülerinnen und
% Schüler in die Schule.
% https://gfx.sueddeutsche.de/apps/e525337/www/_image_desktopw1840q70-1e2e2bf78b7d4430.png
% 18% der Grundschüler in Notbetreuung in BW
%
For our work models\footnotemark we use the reductions in work mobility reported in the
Google Mobility Data \citep{Google2021} to calibrate our work policies.
Reductions in work contacts are not random but governed through a work contact priority
where the policy changes the threshold below which workers stay home.
Figure \ref{fig:work_multiplier} shows the share of workers that go to work in our model
over time.

\begin{figure}[ht]
    \centering
    \includegraphics[width=\textwidth]{../figures/results/figures/data/work_multiplier_since_sep}
    \caption{Share of Workers with Work Contacts}
    \label{fig:work_multiplier}
    \figurenotes{The figure shows the work mobility as reported by \cite{Google2021}. We take this as a proxy of the share of workers who are not in home office, i.e. who still have physical work contacts.}
\end{figure}

@@

\begin{figure}[ht]
    \centering
    \caption{Share of Individuals With Rapid Tests}
    \label{fig:share_ever_rapid_test}
    \begin{subfigure}{.55\textwidth}
      \includegraphics[width=0.9 \textwidth]{../figures/results/figures/scenario_comparisons/spring_fit/full_share_ever_rapid_test}
    \end{subfigure}%
    \begin{subfigure}{.55\textwidth}
      \includegraphics[width=0.9 \textwidth]{../figures/results/figures/scenario_comparisons/spring_fit/full_share_rapid_test_in_last_week}
    \end{subfigure}
    \caption{Share of Individuals Having Done a Rapid Test in the Last Week}
    \label{fig:share_rapid_test_last_week}
    \figurenotes{The figure compares the share of individuals who have ever done a rapid test or done a rapid test within the last week in our simulations to the shares reported in the \href{https://projekte.uni-erfurt.de/cosmo2020/web/topic/wissen-verhalten/80-schnelltests/}{COVID-19 Snapshot Monitoring survey}. The
    left panel compares the share of individuals who have ever done a rapid test. The right panel compares the share of individuals who have done a rapid test within the last seven days in our simulation compared to the share reporting to have done at least weekly rapid tests in the last four weeks in the COSMO survey. Overall our calibration of rapid tests are slightly conservative. The overall share is below that in the study. We fit the share of weekly tests quite exactly. However, the study only covers adults while our share also includes children who are tested very regularly when attending school.
    }
\end{figure}

>>>>

\begin{figure}[ht]
    \centering
    \includegraphics[width=0.9 \textwidth]{../figures/assortative_matching_probability_example}
    \caption{Distribution of random non-work contacts by age of participants.}
    \label{fig:assortativity}
    \figurenotes{
        The figure shows the distribution of random non-work contacts by age groups. A
        row shows the share of contacts a certain age group has with all other age
        groups. Higher values are colored in darker red tones. The diagonal represents
        the share of contacts with individuals from the same age group. }
\end{figure}

@@

In our empirical application we distinguish four groups of contact types: households,
education, work and other contacts. For households we assume that the individuals'
contacts in their households do not change over our estimation period. For nurseries,
preschools and schools we implement vacations as announced by the German federal states
as well as school closures. For the moment we ignore both emergency childcare and that
lack of childcare leads working parents to stay home.
%
% Schließung von Kindertagesstätten und Schulen: 37,4 Millionen ausgefallene Arbeitstage
% http://www.iab-forum.de/schul-und-kitaschliessungen-krankheit-quarantaene-die-coronabedingten-arbeitsausfaelle-der-erwerbstaetigen-steigen-auf-592-millionen-arbeitstage/
%
%
% https://www.sueddeutsche.de/politik/schulschliessung-lockdown-bildung-1.5190377:
% In allen Ländern geht trotz des Lockdowns ein erheblicher Anteil der Schülerinnen und
% Schüler in die Schule.
% https://gfx.sueddeutsche.de/apps/e525337/www/_image_desktopw1840q70-1e2e2bf78b7d4430
% 18% der Grundschüler in Notbetreuung in BW
%
For our work models\footnotemark we use the reductions in work mobility reported in the
Google Mobility Data \citep{Google2021} to calibrate our work policies.
Reductions in work contacts are not random but governed through a work contact priority
where the policy changes the threshold below which workers stay home.
Figure \ref{fig:work_multiplier} shows the share of workers that go to work in our model
over time.

\begin{figure}[ht]
    \centering
    \includegraphics[width=\textwidth]{../figures/results/figures/data/work_multiplier_since_sep}
    \caption{Share of Workers with Work Contacts}
    \label{fig:work_multiplier}
    \figurenotes{The figure shows the work mobility as reported by \cite{Google2021}. We
    take this as a proxy of the share of workers who are not in home office, i.e. who
    still have physical work contacts. The figure interpolates over weekends as we handle
    weekend effects through information on work on weekends in the German census data we
    use.}
\end{figure}

@@

\begin{figure}[ht]
    \centering
    \caption{Share of Individuals With Rapid Tests}
    \label{fig:share_ever_rapid_test}
    \begin{subfigure}{.55\textwidth}
      \includegraphics[width=0.9 \textwidth]{../figures/results/figures/scenario_comparisons/combined_fit/full_share_ever_rapid_test}
    \end{subfigure}%
    \begin{subfigure}{.55\textwidth}
      \includegraphics[width=0.9 \textwidth]{../figures/results/figures/scenario_comparisons/combined_fit/full_share_rapid_test_in_last_week}
    %   \caption{Share of Individuals Having Done a Rapid Test in the Last Week}
    \end{subfigure}
    \label{fig:share_rapid_test_last_week}
    \figurenotes{The figure compares the share of individuals who have ever done a rapid test or done a rapid test within the last week in our simulations to the shares reported in the \href{https://projekte.uni-erfurt.de/cosmo2020/web/topic/wissen-verhalten/80-schnelltests/}{COVID-19 Snapshot Monitoring survey}. The
    left panel compares the share of individuals who have ever done a rapid test. The right panel compares the share of individuals who have done a rapid test within the last seven days in our simulation compared to the share reporting to have done at least weekly rapid tests in the last four weeks in the COSMO survey. Overall our calibration of rapid tests are slightly conservative. The overall share is below that in the study. We fit the share of weekly tests quite exactly. However, the study only covers adults while our share also includes children who are tested very regularly when attending school.
    }
\end{figure}

### 2021-06-05 paper/model/summary.tex
Model description in report mostly done.
Add new results figures.

The structure of the model is depicted in Figure~\ref{fig:model_graph}.

\begin{figure}[!tp]
    \centering
    \includegraphics[width=\textwidth]{../figures/model_detailed.png}
    \caption{Simplified graph of the model.}
    \label{fig:model_graph}
\end{figure}

The background characteristics include age, county and occupation of each simulated
individual. Contact models are functions that map individual characteristics into a
predicted number of contacts. Currently, we distinguish between eight types of contact
models which are all listed in Figure~\ref{fig:model_graph}: households, recurrent and
random work contacts, recurrent and random leisure contacts, and nursery, preschool, and
school contacts.

@@

Once a person is infected, the disease progresses in a fairly standard way which is
depicted in Figure~\ref{fig:course_of_disease}. Asymptomatic cases and cases with mild
symptoms are infectious for some time and recover eventually. Cases with severe symptoms
additionally require hospitalization and lead to either recovery or death.

>>>>

The structure of the model is depicted in Figure~\ref{fig:broad_model_description}.

The background characteristics include age, county and occupation of each simulated
individual. Contact models are functions that map individual characteristics into a
predicted number of contacts. Currently, we distinguish between eight types of contact
models which are all listed in Figure~\ref{fig:broad_model_description}: households,
recurrent and random work contacts, recurrent and random leisure contacts, and nursery,
preschool, and school contacts.

@@

Once a person is infected, the disease progresses in a fairly standard way which is
depicted in Figure~\ref{fig:disease_progression}. Asymptomatic cases and cases with mild
symptoms are infectious for some time and recover eventually. Cases with severe symptoms
additionally require hospitalization and lead to either recovery or death.

### 2021-06-05 paper/report.tex
Add new results figures.

        \includegraphics[width=\textwidth]{../figures/results/figures/scenario_comparisons/combined_fit/full_new_known_case}
        \caption{{\small Recorded cases: Empirical and simulated}}
        \label{fig:aggregated_fit}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../figures/results/figures/data/work_multiplier_since_sep}
        Stringency index + multipliers

        Contact reduction $\times$ hygiene multiplier for different types of contacts

        potentially $\times$ seasonality

        else put seasonality separately
        \begin{itemize}
            \item Work
            \item School
            \item Other
        \end{itemize}

        \caption{{\small Contact reductions}}
        \label{fig:stringency_index}
    \end{subfigure}

@@

        % \includegraphics[width=\textwidth]{../figures/results/figures/scenario_comparisons/combined_fit/full_new_known_case}

        Effects of social structure (implicit tracing) / effects of different types of testing

        \caption{{\small Effects of different types of testing}}
        \label{fig:decomposition_tests}
    \end{subfigure}

@@

    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        % \includegraphics[width=\textwidth]{../figures/results/figures/scenario_comparisons/one_off_and_combined/full_new_known_case_cropped}
        \caption{{\small Effects of different schooling scenarios after Easter}}
        \label{fig:schooling_scenarios_easter}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.475\textwidth}
        \centering

        % \includegraphics[width=\textwidth]{../figures/results/figures/scenario_comparisons/one_off_and_combined/full_newly_infected_cropped}
        \caption{{\small TBD}}
        \label{fig:to_be_determined}
    \end{subfigure}
    \vskip3ex

>>>>

    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../figures/results/figures/scenario_comparisons/combined_fit/full_new_known_case}
        \caption{{\small Recorded cases: Empirical and simulated}}
        \label{fig:aggregated_fit}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../figures/results/figures/data/stringency}

        \textcolor{red}{Where to put seasonality?}
        \caption{{\small Contact reductions}}
        \label{fig:stringency_index}
    \end{subfigure}

@@

        \includegraphics[width=\textwidth]{../figures/results/figures/scenario_comparisons/effect_of_rapid_tests/full_newly_infected}
        \caption{{\small Effects of different types of testing}}
        \label{fig:decomposition_tests}
    \end{subfigure}

@@

    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../figures/results/figures/scenario_comparisons/one_off_and_combined/full_new_known_case_cropped}
        \caption{{\small Effects of different schooling scenarios after Easter}}
        \label{fig:schooling_scenarios_easter}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../figures/results/figures/scenario_comparisons/one_off_and_combined/full_newly_infected_cropped}
        \caption{{\small TBD}}
        \label{fig:to_be_determined}
    \end{subfigure}
    \vskip3ex

### 2021-06-05 paper/results.tex
Add very preliminary Shapley values figure.
Some smallish updates; compile on Linux.
Add new results figures.

\textcolor{red}{The results can be found in `figures/results`. This includes both figures
and tables for lookup of numbers and summary tables}

@@

\begin{figure}[ht]
\centering
\begin{subfigure}{.6\textwidth}
  \includegraphics[width=0.9 \textwidth]{../figures/placeholder}
  %../figures/results/figures/scenario_comparisons/school_scenarios/full_new_known_case
\end{subfigure}%
\begin{subfigure}{.6\textwidth}
  \includegraphics[width=0.9 \textwidth]{../figures/placeholder}
  %../figures/results/figures/scenario_comparisons/school_scenarios/full_newly_infected
\end{subfigure}
\caption{The Effect of Different School Scenarios on Observed and Unobserved Cases}
\figurenotes{\textcolor{red}{K: One of the scenarios starts too early. Will be fixed with the next full simulations run.}}
\label{fig:school_scenarios}
\end{figure}

@@

>>>>

\textcolor{red}{The results can be found in `figures/results`. This includes both figures
and tables for lookup of numbers and summary tables.}

@@

\begin{figure}[ht]
\centering
\begin{subfigure}{.6\textwidth}
  \includegraphics[width=0.9 \textwidth]{../figures/results/figures/scenario_comparisons/school_scenarios/full_new_known_case}
\end{subfigure}%
\begin{subfigure}{.6\textwidth}
  \includegraphics[width=0.9 \textwidth]{../figures/results/figures/scenario_comparisons/school_scenarios/full_newly_infected}
\end{subfigure}
\caption{The Effect of Different School Scenarios on Observed and Unobserved Cases}
\figurenotes{\textcolor{red}{K: One of the scenarios starts too early. Will be fixed with the next full simulations run.}}
\label{fig:school_scenarios}
\end{figure}

@@

\begin{figure}[ht]
\centering
% \includegraphics[width=\textwidth]{../figures/preliminary_shapley}
\caption{Shapley Values}
\figurenotes{\textcolor{red}{K: These are taken from Tobi's notebook as examples. Numbers
might still change}}
\label{fig:school_scenarios}

\end{figure}
